ATHENS course on Extreme-Value Theory

### 2022-03-21 Draft#1.Rmd
draft1

```{r}
n <- gev.fit(dataset[,1])
m <- gev.diag(n)
``
Doubt: Not able to check the profile liklihood 
since X value is -0.13 it follows this distrubution

>>>>

```{r}
var1 <- gev.fit(dataset[,1])
# Xi = -0.135 --> Weibull
m <- gev.diag(var1)
```

```{r}
var2 <- gev.fit(dataset[,2])
# Xi = -0.138 --> Weibull 
n <- gev.diag(var2)

```{r}
var3 <- gev.fit(dataset[,3])
# Xi = -0.086 --> Gumbell
o <- gev.diag(var3)

```{r}
var4 <- gev.fit(dataset[,4])
# Xi = -0.123 --> Weibull
p <- gev.diag(var4)
```

```{r}
var5 <- gev.fit(dataset[,5])
# Xi = -0.129 --> weibull
q <- gev.diag(var5)
```

Doubt: Not able to check the profile liklihood 
since X value is -0.13 it follows this distrubution
calculate x n tell distrbution

mean excess plot left

```{r}
mrl.plot(dataset[,1])
mrl.plot(dataset[,2])
mrl.plot(dataset[,3])
mrl.plot(dataset[,4])
mrl.plot(dataset[,5])
```

<<<<<<<<<<<<<<<<<< Univariate Analysis >>>>>>>>>>>>>>>>>>

ANCOVA Analysis (analysis of covariance)

```{r}
summary(aov(dataset[,1]~dataset[,2]))
```

Scatterplot

Line of best fit

Regression Analysis

whatever else u find relevant

<<<<<<<<< Multivariate analysis >>>>>

we start with scatterplot

```{r}
mydata=dataset[,-1]
pairs(mydata)
```

 Marginal standardization based on the rank transform

```{r}
n=nrow(mydata)
myranks=apply(mydata,2,rank)
data.unif=myranks/(n+1)
data.stand=1/(1-data.unif)
```

Estimation of the extremal coefficient

```{r}
p=0.8+0:19*0.01
u.star=1/(1-p)
u.star[1]*mean(apply(data.stand>u.star[1],1,any))
u.star[20]*mean(apply(data.stand>u.star[20],1,any))
theta.est=c()
for(i in 1:length(p)){
  theta.est[i]=u.star[i]*mean(apply(data.stand>u.star[i],1,any))
}
plot(p,theta.est,type="l",lwd=3,xlab="p",ylab=expression(theta[5]))
# calculate approximate 95% pointwise confidence intervals
sd_est = sqrt(u.star/n * theta.est *(1-theta.est/u.star))
lines(p,theta.est + qnorm(.975)*sd_est, col = "blue", lwd = 3, lty = 2)
lines(p,theta.est - qnorm(.975)*sd_est, col = "blue", lwd = 3, lty = 2)
```
Estimation of the coefficient of tail dependence

```{r}
library(fExtremes)
hillPlot(apply(data.stand,1,min), start=0.8*n, plottype="xi") 
```

### 2022-03-21 Practicals/multivariate2022.Rmd
draft1

```{r, echo=TRUE}
n=200
pars=c(0.5,0.2,0.2,6)
w=rpairbeta(n,dimData=3,par=pars)
plot3d(w,xlab=expression(w[1]),ylab=expression(w[2]),zlab=expression(w[3]))
rglwidget()

@@

We first define the log-likelihood function, and then use it within the maxLik function to compute the maximum likelihood estimate.

>>>>

```{r, echo=TRUE}
n=500
pars=c(0.5,0.2,0.2,6)
w=rpairbeta(n,dimData=3,par=pars)
plot3d(w,xlab=expression(w[1]),ylab=expression(w[2]),zlab=expression(w[3]))
rglwidget()

@@

We first define the log-likelihood function, and then use it within the maxLink function to compute the maximum likelihood estimate.
